Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
evaluation criteria section

\section{Goals/Evaluation Criteria} 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
    \item {\bfseries Time to Completion} Time to completion. 
    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
\end{enumerate}

>>>>

\section{Goals/Evaluation Criteria}
We evaluate the existing and redesigned Tor Browser configuration interface 
through the empirical evaluation and heuristic evaluation criteria below. The
empirical evaluation criteria were considered during our qualitative and 
quantitative user studies, whereas the heuristic evaluation was considered during
the redesign process.

Since there is risk associated with making an unobfuscated 
connection with the Tor network, the configuration process is not automated.
Our empirical evaluation criteria for the Tor Browser configuration
interface are from common metrics that measure ease of use with a special 
consideration for high-risk users: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
    \item {\bfseries Time to Completion} Time to completion. 
    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
\end{enumerate}

A heuristic evaluation is a rule-based evaluation which leverages standards
developed over trial and error that have shown to work in the User Interface design 
community. We draw from Jacob Nielsen's ten heuristics ({\color {red} CITE THIS}
and other industry standards to form the following heuristic evaluation criteria: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
    \item {\bfseries Visibility of System Status} provide feedback on what the system is doing.
    \item {\bfseries User Control and Freedom} allow users to override system, supports undo and redo actions. 
    \item {\bfseries Understandable Language} ~6th grade reading level. 
    \item {\bfseries Minimal Design} surpressing rarely used information to reduce cognitive load. 
    \item {\bfseries Error Management} expressing errors in plain language and offering a solution. 
    \item {\bfseries Help and Documentation} provide contextual help and easy access to information. 
\end{enumerate}

An empirical evaluation of the problems with the existing Tor Browser 
configuration interface through user observation and interviews can be 
found in section {\color{red} TODO}. A heuristic evaluation of the existing interface
and new interface can be found  in section {\color{red} TODO}. We empirically show 
that the redesigned interface improves completion rate, reduces time to completion, 
and provides a safe path for at-risk users in section {\color{red} TODO}.
